```{r}
library(tidyverse)
```
```{r}
logs <- read_csv("https://dwillis.github.io/sports-data-files/footballlogs1124.csv")
glimpse(logs)
```
```{r}
logs <- logs |>
  mutate(point_differential = TeamScore - OpponentScore)
logs |>
  summarise(correlation = cor(point_differential, Penalties, method = "pearson"))
model_simple <- lm(point_differential ~ PenaltyYds, data = logs)
summary(model_simple)
```
##It gave me a P-value of -0.019. That means that as penalties increase, the point differential tends to decrease (teams with more penalties score slightly fewer points relative to their opponent). The R-squared value is under 0.03, which means penalty yards explain only about 0.03 % of the variation in score differential — effectively none. That means penalty yards are essentially useless for predicting who wins or by how much in this dataset.
```{r}
logs |>
  select(point_differential, Penalties, PenaltyYds, Fumbles, Interceptions) |>
  cor(method = "pearson", use = "complete.obs")
```
```{r}
model_multi <- lm(point_differential ~ Penalties + PenaltyYds + Fumbles + Interceptions,
                  data = logs)
summary(model_multi)
```
###I built a multiple regression model predicting point differential using Penalties, PenaltyYds, Fumbles, and Interceptions. All predictors were statistically significant, but there is a risk of multicollinearity, especially between penalties and penalty yards, because thy are related, penalty yards has a small positive coefficient despite being a negative play, likely due to its correlation with penalties.
```{r}
close_games <- logs |>
  filter(abs(point_differential) <= 7)
```

```{r}
model_simple_close <- lm(point_differential ~ PenaltyYds, data = close_games)
summary(model_simple_close)
```


```{r}
model_multi_close <- lm(point_differential ~ Penalties + PenaltyYds + Fumbles + Interceptions,
                        data = close_games)
summary(model_multi_close)
```
###I think the multiple model is better because the r-squared and the correlation seems to be more accurate than when we used the simple model.
