```{r}
library(tidyverse)
```
```{r}
wbb_stats <- read_csv("https://dwillis.github.io/sports-data-files/wbbstats1525.csv")
```
```{r}
wbb_pergame <- wbb_stats |>   
  mutate(
    points_pg    = ForPoints / Games,       
    rebounds_pg  = TotalRebounds / Games,    
    assists_pg   = Assists / Games,      
    steals_pg    = Steals / Games  
  ) |>
  select(Season, School,
         points_pg, rebounds_pg, assists_pg, steals_pg)
```

```{r}
wbb_zscores <- wbb_pergame |>
  group_by(Season) |>
  mutate(
    z_points   = (points_pg   - mean(points_pg,   na.rm = TRUE)) / sd(points_pg,   na.rm = TRUE),
    z_rebounds = (rebounds_pg - mean(rebounds_pg, na.rm = TRUE)) / sd(rebounds_pg, na.rm = TRUE),
    z_assists  = (assists_pg  - mean(assists_pg,  na.rm = TRUE)) / sd(assists_pg,  na.rm = TRUE),
    z_steals   = (steals_pg   - mean(steals_pg,   na.rm = TRUE)) / sd(steals_pg,   na.rm = TRUE),
    composite_z = (z_points + z_rebounds + z_assists + z_steals) / 4
  ) |>
  ungroup() |>
  arrange(desc(composite_z))
```

```{r}
maryland_zscore <- wbb_zscores |>
  filter(School == "Maryland") |>
  arrange(desc(composite_z))
```


##I think the best story idea is why the hell is Sacramento State so high up haha. Just kidding, I think looking at the analysis of how dynasties have shifted across the past decade would be a particualrly interesting look, especially considering the sport of WBB. Sorry this is late, with it being Yom Kippur, I went home for the weekend, so didn't get a chace to do this.

## They've had just four NCAA tournament apperances in program history, have never made it past the first round and have never been ranked. But statistically, they're on par with the women's basketball dynasties like UConn, Baylor and South Carolina. The Troy Trojans over the past decade have been one of the best teams in the Sun Belt for years, but other than that, have been a relatively ho-hum program under coach Chanda Rigby. But research found that the Trojans have had five of the top-30 statistically dominant teams over the past decade. That's more than over 95% of D1 schools. So what's made them so dominant. For one, they beat up on conference opponents. In a three-year strech from 2021 to 2023, Troy lost a combined six Sun Belt games. They also score a lot of points, over 80 per game. But the last thing, Troy REBOUNDS. They have been the best rebounding team for almost every year since 2019. 